Synthesising Recursive Functions for First-Order Model Counting

### 2023-02-16 doc/paper/paper.tex
A slide about applications
Initial draft of the function-building algorithm

>>>>

\begin{algorithm}[t]
  \caption{Construct functions from an FCG}
  \SetKwProg{Fn}{Function}{:}{}

  \SetKwData{domains}{domains}
  \SetKwData{functionCall}{call}
  \SetKwData{functionSignature}{signature}
  \SetKwData{functionNames}{F}
  \SetKwData{variableNames}{V} % TODO: mathcal? Same for function names?
  \SetKwData{newVariableNames}{V'}
  \SetKwData{expression}{e}
  \SetKwData{functions}{funs}

  \SetKwFunction{newFunctionName}{newFunctionName}
  \SetKwFunction{newVariableName}{newVarName}
  \SetKwFunction{visit}{visit}
  \SetKwFunction{actuallyVisit}{actuallyVisit}

  \KwIn{$\mathcal{D}$---the set of domains of the input formula}
  \KwIn{$s$---the source of the FCG}
  \KwData{$\functionNames = \emptyset$}
  \KwOut{a list of Strings, each defining a function (the top one is the main one)}
  $\variableNames \gets \{\, d \mapsto \newVariableName{} \mid d \in \mathcal{D} \,\}$\;
  \uIf{$s$ is a direct successor of a $\Reff$ node}{
    $(\expression, \functions) \gets \visit{$s$, $\variableNames$}$\;
    \Return{\functions}\;
  }
  \Else{
    $f \gets \newFunctionName{$s$}$\;
    $(\expression, \functions) \gets \visit{$s$, $\variableNames$}$\;
    \Return{$\langle f(\langle \variableNames{$d$} \mid d \in \mathcal{D} \rangle) = \expression \rangle + \functions$}\;
  }
  \Fn{\visit{node $v$, \variableNames}}{
    \If{$v$ is not a direct successor of a $\Reff$ node}{ % TODO: boldface the NOT
      \Return{\actuallyVisit{$v$, \variableNames}}\;
    }
    $f \gets \newFunctionName{$v$}$\;
    $\newVariableNames \gets \{\, \text{if } d \in v.\domains \text{ and } n \text{ contains subtraction then } d \mapsto \newVariableName{} \text{ else } d \mapsto n \mid d \mapsto n \in \variableNames \,\}$\;
    $(\expression, \functions) \gets \actuallyVisit{$v$, \newVariableNames}$\;
    $\functionCall \gets f(\langle \variableNames{$d$} \mid d \in v.\domains \rangle)$\;
    $\functionSignature \gets f(\langle \newVariableNames{$d$} \mid d \in v.\domains \rangle)$\;
    \Return{$(\functionCall, \langle \functionSignature = \expression \rangle + \functions)$}\;
  }
  \Fn{\actuallyVisit{node $v$, \variableNames}}{
    \Switch{type of $v$}{
      \uCase{$\Reff_{\rho}(v')$}{
        \Return{$(\functionNames{$v'$}(\langle \variableNames{$\rho(d)$} \mid d \in v'.\domains \rangle), \langle \rangle)$}\;
      }
      \lCase{$\GDR(v')$}{\Return{\visit{$v'$, \variableNames}}}
      \uCase{$\CR_{d,d'}(v')$}{\Return{\visit{$v'$, $\variableNames \cup \{\, d' \mapsto (\variableNames(d) - 1) \,\}$}}\;}
      \dots
    }
  }
\end{algorithm}
% TODO: introduce symbol for list concatenation (4 places)
% 'is a direct successor of a Ref node' = the in-degree is > 1
% TODO: check if the distinction between data and function is appropriate and that all function calls use the right {} syntax
% TODO: DeclareMathOperator for Or, etc.
% TODO: check if all semicolons are there

\begin{itemize}
  \item for each node v, v.domains is a precomputed set of domains that are used
        by v and all of its successors (except the ones that are introduced by v
        or its successors) (this was already part of ForcLift, although had to
        be reimplemented in a way that avoids infinite loops when dealing with
        cycles in graphs)
  \item NOTE: for list generators over a set of domains, we assume an arbitrary
        fixed ordering over all domains
  \item functionNames is a partial map (initially empty) from the set of nodes
        of the FCG to Strings
  \item newVariableName() just generates a unique identifier for a variable
  \item newFunctionName(node n) does the same thing for function names and also
        records the new name in functionNames
\end{itemize}
